---
title: "Bayeshrimp"
author: "Jaber Belkhiria"
date: "Nov 28, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r, echo=T}
library(rmarkdown)
library(Hmisc)
library(psych)
library(tableone)
library(plyr)
library(fitdistrplus)
library(tm)
library (ggmap)
library(maps)
library(sp)
library(plyr)
library(FactoMineR)
library(devtools)
library(tableone)
library(fitdistrplus)
library(epiDisplay)
library(rpart)
library(epiDisplay)
library(rethinking)
library(rstan)
library(loo)
library(bayesplot)
library(rstanarm) 
#devtools::install_github("rstudio/rmarkdown")
```

```{r, echo=FALSE}
options(encoding="latin1") # read french
getwd()
setwd("~/Box Sync/epi 208/for irina")
#Importind data  set
Data<- read.csv("data_1.csv",encoding="UTF8towcs")
#Changed empty cells and IND to NA so R can understand it 
Data[Data=="IND"]<-NA
Data[Data==""]<-NA
```

#
```{r, echo=T}
#curious to see how many null variables I have
Hmisc::describe(Data)

#I looked at missing data and now I'm going to remove columns with a high number of missing (over 200)
Data.c <- subset(Data, select = c(id,Longitude,Latitude,JLSA,A1,A3,A9,A10,B3,B4,C1,C2,C7,D2,D5,D6,F3,F5,G2,I14,I22,I23,I24,I25,H6,H8) )
#curious to see how many null variables I have
#Hmisc::describe(Data.c)
write.csv(Data.c, file = "Data.c_1.csv")
dc<- read.csv(file="Data.c_1.csv", header=TRUE, sep=",")
```

```{r, echo=T}
#data cleaning
dc$Latitud<-as.numeric(dc$Latitud)
dc$Longitud<-as.numeric(dc$Longitud)
#binary variables variables

tmp<-as.character(dc$A1)
tmp[tmp=="Si"]<-"1"
dc$A1<-factor(tmp)

tmp<-as.character(dc$A3)
tmp[tmp=="Si"]<-"1"
dc$A3<-factor(tmp)

tmp<-as.character(dc$A9)
tmp[tmp=="Si"]<-"1"
dc$A9<-factor(tmp)

tmp<-as.character(dc$B3)
tmp[tmp=="Si"]<-"1"
dc$B3<-factor(tmp)

tmp<-as.character(dc$B4)
tmp[tmp=="Si"]<-"1"
dc$B4<-factor(tmp)

tmp<-as.character(dc$C1)
tmp[tmp=="Si"]<-"1"
dc$C1<-factor(tmp)

tmp<-as.character(dc$C2)
tmp[tmp=="Si"]<-"1"
dc$C2<-factor(tmp)

tmp<-as.character(dc$D2)
tmp[tmp=="Si"]<-"1"
dc$D2<-factor(tmp)

tmp<-as.character(dc$D5)
tmp[tmp=="Si"]<-"1"
dc$D5<-factor(tmp)

tmp<-as.character(dc$I14)
tmp[tmp=="Si"]<-"1"
dc$I14<-factor(tmp)

tmp<-as.character(dc$I22)
tmp[tmp=="Si"]<-"1"
dc$I22<-factor(tmp)

tmp<-as.character(dc$I23)
tmp[tmp=="Si"]<-"1"
dc$I23<-factor(tmp)

tmp<-as.character(dc$I24)
tmp[tmp=="Si"]<-"1"
dc$I24<-factor(tmp)

tmp<-as.character(dc$I25)
tmp[tmp=="Si"]<-"1"
dc$I25<-factor(tmp)

tmp<-as.character(dc$H6)
tmp[tmp=="Si"]<-"1"
dc$H6<-factor(tmp)

#Continuous
dc$F3[dc$F3==1616]<-16
dc$F5[dc$F5==500]<-5

tmp<-as.character(dc$F5)
tmp[tmp=="7.5/M2"]<-"7.5"
tmp[tmp=="10/M2"]<-"10"
dc$F5<-as.numeric(tmp)

tmp<-as.character(dc$G2)
tmp[tmp=="2 a?os"]<-"2"
tmp[tmp=="17. A?os"]<-"17"
tmp[tmp=="21. A?os"]<-"21"
dc$G2<-as.numeric(tmp)

#fixing cATEGORICAL VARIABLES 
levels(dc$A9)
levels(dc$A9) <- c("0", "1","2", "3")
#low levels thus I had to collapse 0 and 2
levels(dc$A9) <- c("0", "1","0", "2")

levels(dc$A10)
levels(dc$A10) <- c("0", "1","2", "3")
#low levels thus I had to collapse 0 and 2
levels(dc$A10) <- c("0", "1","0", "2")

levels(dc$D6)
levels(dc$D6) <- c("4","2","0","0","3","2","2","2","2","2","0","1","2")
levels(dc$C7)
levels(dc$C7) <- c("1", "0", "0","0", "0","0","2","0", "0")

dc$F3[dc$F3==1616]<-16

dc$F5[dc$F5==500]<-5

dc$JSLA<-as.factor(dc$JLSA)
levels(dc$JLSA)
#############
# Mapping
dc$H6<- factor(dc$H6, labels = c("Negative","Positive","Not available"),exclude=NULL)
dc_clean<- subset(dc, Latitude > 0)
Positive= subset(dc_clean,H6 == 'Positive')
Negative= subset(dc_clean,H6== 'Negative')
Not_available= subset(dc_clean,H6== 'Not available')

dc_clean$H6
levels(dc_clean$H6)
```

#
```{r, echo=F}
map<-qmap(location = c(-108.61083984375,24.146753594703075),zoom=7, legend = 'topright')
map +geom_point(aes(x = Longitude, y = Latitude,colour =H6),size=3,alpha=0.5, data = dc_clean,name="farms",exclude=NULL )+
  geom_point()+ scale_color_manual(values = c("Positive" = 'red','Negative' = 'green',"Not available"= "blue"))
```

#A quick stacked bar plot to see sample vary per year and per test result (positive/ negative)
```{r, echo=F}
#now I'm going to eliminate row without outcome and see what would happen
dc1 <- dc[!is.na(dc$H6), ]

#Checking df now
Hmisc::describe(dc1)

#colinearity
#pairs(dc1)
```
#A quick stacked bar plot to see sample vary per year and per test result (positive/ negative)
```{r, echo=F}
#Creating a table one 
## List numerically coded categorical variables
factorVars <- c('JLSA','A1','A3','A9','A10','B3','B4','C1','C2','C7','D5','D6','I14','I22','I23','I24','I25')

## Create a variable list. Use dput(names(pbc))
vars <- c('JLSA','A1','A3','A9','A10','B3','B4','C1','C2','C7','D5','D6','I14','I22','I23','I24','I25',"F3","F5","G2")
## Create Table 1 stratified by H6 (omit strata argument for overall table)
library(tableone)
tableOne <- CreateTableOne(vars = vars, strata = "H6", data = dc1, factorVars = factorVars)
table2<- CreateTableOne(vars = vars, data = dc1, factorVars = factorVars)
summary(table2$ContTable)
tableOne
tableOne$CatTable
tableOne$ContTable
summary(tableOne$ContTable)
summary(tableOne$CatTable)
```

```{r, echo=F}
               
#Hist
hist(dc1$F3,main='F3')
hist(dc1$F5,main='F5')
hist(dc1$G2,main='G2')
#####log F3###
log_F3<-log(dc1$F3)
hist(log_F3,main='F3',breaks=15,prob=T)
lines(density(log_F3, na.rm = T, from = 0, to =max(log_F3, na.rm = T) ))
#####Log F%############
log_F5<-log(dc1$F5)
hist(log_F5,main='F5',breaks=15,prob=T)
lines(density(log_F5, na.rm = T, from = 0, to =max(log_F5, na.rm = T) ))
curve(dnorm(x, mean=mean(log_F5), sd=sd(log_F5)), add=TRUE)
```
#
```{r, echo=F}
library(fitdistrplus)
#determining the distribution of my data
descdist(as.numeric(na.omit(dc1$G2)), discrete = FALSE)
```

#Mapping positve and Negative samples over the whole time period.
```{r, echo=F}
#############Attempting a CART##############
library(rpart)
fit <- rpart(dc1$H6~., data=dc1[6:25],method="anova")
printcp(fit) # display the results 
plotcp(fit) # visualize cross-validation results
summary(fit) # detailed summary of splits
# create additional plots
par(mfrow=c(1,2)) # two plots on one page
rsq.rpart(fit) # visualize cross-validation results  
dev.off()
# plot tree
plot(fit, uniform=TRUE,
     main="Regression Tree for Mexus ")
text(fit, use.n=TRUE, all=TRUE, cex=.8)

# prune the tree
pfit<- prune(fit, cp=0.01160389) # from cptable   

# plot the pruned tree
plot(pfit, uniform=TRUE,
     main="Pruned Regression Tree for Mexus")
text(pfit, use.n=TRUE, all=TRUE, cex=.8)

#top variables I22,I25,D5,I24,A10,A9,B3
#####################################################################
##### selection of the best model and dealing with confounders #######
######################################################################
EJs<-dc1[,c("I22","I25","D5","I24","A10","A9","B3","H6")] 
```


#I was curious to do a staked bar plot and check how the AI subtypes are spread over the year
```{r, echo=T}

# maximum (saturated model) ###
fit.full<-glm(EJs$H6~., data=EJs, family=binomial(link="logit"))
summary(fit.full)
lroc(fit.full, auc.coords=c(0.2,0.1),cex=0.8)$auc
#logistic.display(fit.full)
#vif(fit.full) #no multicollinearity obsv#
step(fit.full, direction="backward")    ## use help(step) to have a look at it ##
step(fit.full, direction="forward") 

# Reduced model  ###
fit.reduced<-glm(H6~ I22+D5+I24+A10+B3, data=EJs, family=binomial(link="logit"))
summary(fit.reduced)
lroc(fit.reduced, auc.coords=c(0.2,0.1),cex=0.8)$auc
logistic.display(fit.reduced)
```

#Mapping Positive samples month per month
```{r, echo=F}

#######Bayesian model
library(rethinking)
#eliminating Na, appreantly this method doesn't work with missing data
EJs.na<- na.omit(dc1[,c('JLSA',"I22","I25","D5","I24","A10","A9","B3","H6")] )

#releveling JLSA
levels(EJs.na$JLSA)
tmp<-as.character(EJs.na$JLSA)
tmp[tmp=="Ahome"]<-"1"
tmp[tmp=="Angostura"]<-"2"
tmp[tmp=="Eldorado"]<-"3"
tmp[tmp=="Escuinapa"]<-"4"
tmp[tmp=="Guasave Norte"]<-"5"
tmp[tmp=="Guasave Sur"]<-"6"
tmp[tmp=="Mazatlàn-San Ignacio"]<-"7"
tmp[tmp=="Navolato Norte"]<-"8"
tmp[tmp=="Navolato Sur"]<-"9"
tmp[tmp=="Rosario"]<-"10"
EJs.na$JLSA<-factor(tmp)
#releveling H6
tmp<-as.character(EJs.na$H6)
tmp[tmp=="Negative"]<-"0"
tmp[tmp=="Positive"]<-"1"
EJs.na$H6<-factor(tmp)
```

```{r positive, fig.width=10, fig.height=10,echo=F}

EJs.na<-data.frame(sapply(EJs.na, function(x) as.integer(as.character(x))))
m.10.3<-rethinking::map(
  alist(
    H6~dbinom(1,p),
    logit(p)<-a+b2*I22+b5*I25+bd*D5+b4*I24+ba*A10+b9*A9+b3*B3,
    a~dnorm(0, 1) ,
    b2~dnorm(0, 1) ,
    b5~dnorm(0, 1) ,
    bd~dnorm(0, 1) ,
    b4~dnorm(0, 1) ,
    ba~dnorm(0, 1) ,
    b9~dnorm(0, 1) ,
    b3~dnorm(0, 1) 
  ),
  data=EJs.na
)
precis(m.10.3)
m10.3stan<-map2stan(m.10.3,data=EJs.na,chains=4,iter=1e4,warmup = 1000)
precis(m10.3stan)
plot(m10.3stan)

#multilevel/ This one did not work so I had to go through stan
start <- c(a = 0, b2 = 0, b3 = 0, b4 = 0, b9 = 0, b5 = 0, bd = 0, ba = 0)
#
#EJs.na$JLSA<-(as.numeric(EJs.na$JLSA))
#EJs.na$H6<-(as.numeric(EJs.na$H6)-1)
#EJs.na$I22<-(as.numeric(EJs.na$I22)-1)
#EJs.na$I25<-(as.numeric(EJs.na$I25)-1)
#EJs.na$D5<-(as.numeric(EJs.na$D5)-1)
#EJs.na$I24<-(as.numeric(EJs.na$I24)-1)
#EJs.na$A10<-(as.numeric(EJs.na$A10)-1)
#EJs.na$A9<-(as.numeric(EJs.na$A9)-1)
#EJs.na$B3<-(as.numeric(EJs.na$B3)-1)
#
#m10.4 <- map2stan( 
#                   alist(
#                     H6~dbinom(1,p),
#                     logit(p) <- #a+a_JSLA[JLSA]+b2*I22+b5*I25+bd*D5+b4*I24+ba*A10+b9*A9+b3*B3,
#                     a_JSLA[JLSA] ~ dnorm(0,sigma_JLSA),
 #                    a~dnorm(0, 10),
  #                   b2~dnorm(0, 10) ,
   #                  b5~dnorm(0, 10) ,
    #                 bd~dnorm(0, 10) ,
     #                b4~dnorm(0, 10) ,
      #               ba~dnorm(0, 10) ,
       #              b9~dnorm(0, 10) ,
        #             b3~dnorm(0, 10) ,
         #            sigma_JLSA ~ dcauchy(0,1)
          #         ) ,
           #        data=EJs.na,chains=3,iter=3000,warmup = 1000,cores=3,start = #start,control=list(adapt_delta=0.99))
#precis( m10.4 , depth=2 )
#plot(m10.4)
#str(EJs.na)

#
#start1 <- c(a = 0, b2 = 0, b5 = 0, bd = 0,b4 = 0, ba = 0, b9 = 0, b3 = 0,alfa = 0)
#m10.5 <- map2stan( 
#  alist(
#    H6~dbinom(1,p),
#    logit(p) <- a+a_JSLA[JLSA]+b2*I22+b5*I25+bd*D5+b4*I24+ba*A10+b9*A9+b3*B3,
#    a~dnorm(0, 10),
#    a_JSLA[JLSA] ~ dnormNC(alfa),
#    b2~dnorm(0, 10) ,
#    b5~dnorm(0, 10) ,
#    bd~dnorm(0, 10) ,
#    b4~dnorm(0, 10) ,
#    ba~dnorm(0, 10) ,
#    b9~dnorm(0, 10) ,
#    b3~dnorm(0, 10) ,
#    alfa ~ dcauchy(0,1)
#  ) ,
#  data=EJs.na,chains=1,iter=3000,warmup = 1000,cores=1,start=start1)

#precis( m10.5 , depth=2 )
#plot(m10.5)
#str(EJs.na)
```

```{r, echo=F}
########
EJs.na$ID<- 1:length(EJs.na)
#Creating the list
d <- list(H6=EJs.na$H6, n=length(EJs.na$H6),
          N_JSLA=length(unique(EJs.na$JLSA)),
          JSLA=EJs.na$JLSA,
          I22=EJs.na$I22,
          I25=EJs.na$I25,
          D5=EJs.na$D5,
          I24=EJs.na$I24,
          A10=EJs.na$A10,
          A9=EJs.na$A9,
          B3=EJs.na$B3)

# Let's deal with divergent transitions and lack of convergence
# We need to get to work with stan code here

code1 <-" 
data{
int<lower=1> n;
int<lower=1> N_JSLA;
int H6[n];
int JSLA[n];
int I22[n];
int I25[n];
int D5[n];
int I24[n];
int A10[n];
int A9[n];
int B3[n];
}
parameters{
vector[N_JSLA] a_JSLA_raw;
real a;
real<lower=0> sigma_JSLA;
real b5;
real bd;
real b2;
real b4;
real ba;
real b9;
real b3;
}
transformed parameters{
vector[N_JSLA] a_JSLA;
a_JSLA = 0 + a_JSLA_raw*sigma_JSLA;//implies a_JSLA ~ normal(0, sigma_JSLA)
}

model{
vector[n] p;
sigma_JSLA ~ cauchy( 0 , 1 );
a ~ normal( 0 , 1 );
a_JSLA_raw ~ normal( 0 , 1 );
b2 ~ normal( 0 , 1 );
b5 ~ normal( 0 , 1 );
bd~ normal( 0 , 1 );
b4~ normal( 0 , 1 );
ba~ normal( 0 , 1 );
b9~ normal( 0 , 1 );
b3~ normal( 0 , 1 );

for ( i in 1:n ) {
p[i] = a + a_JSLA[JSLA[i]]+b2*I22[i]+b5*I25[i]+bd*D5[i]+b4*I24[i]+ba*A10[i]+b9*A9[i]+b3*B3[i];

}
H6 ~ binomial_logit( 1 , p );
}
generated quantities{
vector[n] p;
vector[n] log_lik;

for ( i in 1:n ) {
p[i] = a + a_JSLA[JSLA[i]]+b2*I22[i]+b5*I25[i]+bd*D5[i]+b4*I24[i]+ba*A10[i]+b9*A9[i]+b3*B3[i];
log_lik[i] = binomial_logit_lpmf(H6[i]|1,p[i]);
}

}

"

# Adding variables for stan model
```

```{r Negative, fig.width=10, fig.height=10,echo=F}

options(mc.cores = parallel::detectCores())
m1.1 <- stan(model_code = code1, data=d, iter=3000, chains=4,cores=4, thin=1,
             warmup=1000, control = list(adapt_delta = 0.9, stepsize=1))
```

#Mapping both positive and negative
```{r , fig.width=10, fig.height=10,echo=F}

# Diagnostics: traceplot, No effective samples and Rhat
print(m1.1, probs=c(0.025, 0.975))
traceplot(m1.1, pars=c("a_JSLA","a","sigma_JSLA"))
traceplot(m1.1, pars=c("b2","b5","bd","b4","ba","b9","b3"))
# Information criteria
library(loo)
log_lik1.1 <- extract_log_lik(m1.1)
(m1.1_loo <- loo(log_lik1.1))
waic(log_lik1.1)
```

```{r , fig.width=10, fig.height=10,echo=F}

# extract Stan samples from posterior distribution of this reparameterized model
postm1.1 <- extract(m1.1)
hist(postm1.1$a)
hist(postm1.1$b5)

p<- postm1.1$p  
a_JSLA<- postm1.1$a_JSLA
sigma_JSLA<- postm1.1$sigma_JSLA
b2 <- postm1.1$b2
b5<- postm1.1$b5
bd <- postm1.1$bd
b4<- postm1.1$b4
ba <- postm1.1$ba
b9 <- postm1.1$b9
b3 <- postm1.1$b3
#sim 
```

```{r , fig.width=10, fig.height=10,echo=F}

# Diagnostic !!!
library(shinystan)
options(shinystan.rstudio = TRUE)
launch_shinystan(m1.1) # WOAAAAAA!!!!!!!!
#
# extract Stan samples from posterior distribution of this reparameterized model
post <- extract.samples(m1.1)

#Don't know what to do next in terms of simulating data and playing with that
```
#library(bayesplot)

#JLSA
#counties my different levels (10 of them)
#I22 (B2)
#Is there a water treatment system inside the tanks? (y/n)
#I25 (B5)
#Is your waste water exit located close to the water entrance of your farm? (y/n)
#D5 (bd)
#In the last 10 years did you use organisms that came from imported nurseries? (y/n)
#I24 (b4)
#Are there shrimp farms or processing farms which wastes could affect the water your farm use?(y/n)
#A10 (ba)
#How did you discarded the trash in 2015? (good/bad)
#A9 (b9)
#How did you eliminate the dead organisms in 2014? (good/bad)
#B3 (B3)
#Did you clean /scrape the bottom of the shrimp tank in 2014?